---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
```

# Linear Sufficient Dimension Reduction

The 'linearsdr' package contains popular methods for sufficient dimension reduction as well as some more recent methods in the forthcoming paper "Generalized Forward Sufficient Dimension Reduction for Categorical and Ordinal Responses".

# Installation

The package can be installed by running:

<!-- ::: .pkgdown-devel -->
```{r, eval = FALSE}
# Install development version from GitHub
devtools::install_github("HarrisQ/linearsdr")
```
<!-- ::: -->



The 'NAMESPACE - no oxy' is the original NAMESPACE file prior to when I started using rOxygen and is kept as a reference.
The 'NAMESPACE - oxy' is NAMESPACE file generated from rOxygen.


Current State of Package:
----
* Things that work:
    + Forward Linear SDR methods: OPG/OPCG, MAVE/MADE, Tuning OPCG  
    + Inverse Linear SDR methods: SIR, DR, SAVE with options for regularization  
* Minor Things to do:
    + Clean up OPG/OPCG and MAVE/MADE code  
    + (Maybe) Limit function exports to just the ones people will use  
    + (Maybe) Clean Regularized OPG/OPCG (RADE) Code  

* Major Things to do:
    + Write Vignettes/Examples   
    + Finish code for Multivariate Continuous Response   
    + Write more Documentation for functions  




