---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
```

# Linear Sufficient Dimension Reduction

The 'linearsdr' package contains popular methods for sufficient dimension reduction as well as some more recent methods in the forthcoming paper "Generalized Forward Sufficient Dimension Reduction for Categorical and Ordinal Responses".

## Installation

The package can be installed by running:

<!-- ::: .pkgdown-devel -->
```{r, eval = FALSE}
# Install development version from GitHub
devtools::install_github("HarrisQ/linearsdr")
```
<!-- ::: -->


Current State of Package:
----

* Current features of the package:
    + Forward Linear SDR methods: OPG/OPCG, MAVE/MADE, Tuning OPCG  
    + Inverse Linear SDR methods: SIR, DR, SAVE with options for regularization  

* Immediate tasks to complete:
    + Write Vignettes/Examples   
    + Finish code for Multivariate Continuous Response   
    + Write more Documentation for functions  

* Not-so pressing tasks to complete:
    + Clean up OPG/OPCG and MAVE/MADE code  
    + Limit function exports to just the ones people will use  
    + Clean Regularized OPG/OPCG (RADE) Code  





